---
title: "Wealth Inequality in the Eurozone - Data Observations"
author: ""
date: '19 April 2018'
output: html_document
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
#options(width = 8000)

library(scales)

source("R/functions/utils.R")
source("R/functions/descriptives.R")

formPerc <- function(x){
  nm <- names(x)
  x <- percent(x)
  names(x) <- nm
  x
}
```

```{r include=FALSE, cache=TRUE}
# Import
Wealthfiles <- bigImport()
allCountries <- unique(Wealthfiles[[1]]$country)
```

```{r include=FALSE, cache=TRUE}
# Ginis
Gini_netwealth <- allCountries %>%
  sapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_Gini(
        dset,
        cntr=cnt,
        wealthvar = "net_wealth",
        filters = filter_both # age and non-negative
      )
    })
  })

Gini_liquidassets <- allCountries %>%
  sapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_Gini(
        dset,
        cntr=cnt,
        wealthvar = "liquid_assets",
        filters = filter_both # age and non-negative
      )
    })
  })

Gini_offshore <- allCountries %>%
  sapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_Gini(
        dset,
        cntr=cnt,
        wealthvar = "offshore_wealth",
        filters = filter_both # age and non-negative
      )
    })
  })

Gini_offshore_liquid <- allCountries %>%
  sapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_Gini(
        dset,
        cntr=cnt,
        wealthvar = "liquid_offshore_wealth",
        filters = filter_both # age and non-negative
      )
    })
  })

```


```{r include=FALSE, cache=TRUE}
# Tables

Prop_netwealth <- allCountries %>%
  lapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_WPercentile(
        dset,
        cntr=cnt,
        wealthvar = "net_wealth",
        filters = filter_age,  # age and non-negative
        descending = T # richest to poorest
      )
    })
  }) 
names(Prop_netwealth) <- allCountries

Prop_liquidassets <- allCountries %>%
  lapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_WPercentile(
        dset,
        cntr=cnt,
        wealthvar = "liquid_assets",
        filters = filter_age, # age and non-negative
        descending = T #richest to poorest
      )
    })
  })
names(Prop_liquidassets) <- allCountries


Prop_offshoreweath <- allCountries %>%
  lapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_WPercentile(
        dset,
        cntr=cnt,
        wealthvar = "offshore_wealth",
        filters = filter_age, # age and non-negative
        descending = T #richest to poorest
      )
    })
  })
names(Prop_offshoreweath) <- allCountries

Prop_offshoreweath_liquid <- allCountries %>%
  lapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_WPercentile(
        dset,
        cntr=cnt,
        wealthvar = "liquid_offshore_wealth",
        filters = filter_age, # age and non-negative
        descending = T #richest to poorest
      )
    })
  })
names(Prop_offshoreweath_liquid) <- allCountries

Prop_netwealth_asc <- allCountries %>%
  lapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_WPercentile(
        dset,
        cntr=cnt, 
        probs = seq(0,1,0.001),
        wealthvar = "net_wealth",
        filters = filter_age, # age and non-negative
        descending = F # poorest to richerst
      )
    })
  }) 
names(Prop_netwealth_asc) <- allCountries

Prop_liquidassets_asc <- allCountries %>%
  lapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_WPercentile(
        dset,
        cntr=cnt,
        probs = seq(0,1,0.001),
        wealthvar = "liquid_assets",
        filters = filter_age, # age and non-negative
        descending = F #richest to poorest
      )
    })
  })
names(Prop_liquidassets_asc) <- allCountries


Prop_offshorewealth_asc <- allCountries %>%
  lapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_WPercentile(
        dset,
        cntr=cnt,
        probs = seq(0,1,0.001),
        wealthvar = "offshore_wealth",
        filters = filter_age, # age and non-negative
        descending = F #richest to poorest
      )
    })
  })
names(Prop_offshorewealth_asc) <- allCountries

Prop_liquidoffshorewealth_asc <- allCountries %>%
  lapply(function(cnt) {
    mi_point(Wealthfiles, FUN = function(dset) {
      calc_WPercentile(
        dset,
        cntr=cnt,
        probs = seq(0,1,0.001),
        wealthvar = "liquid_offshore_wealth",
        filters = filter_age, # age and non-negative
        descending = F #richest to poorest
      )
    })
  })
names(Prop_liquidoffshorewealth_asc) <- allCountries
```

```{r include=FALSE}
# WtoI
# WtoI_netwealth <- allCountries %>%
#   lapply(function(cnt) {
#     mi_point(Wealthfiles, FUN = function(dset) {
#       calc_WtoI(
#         dset,
#         cntr=cnt,
#         wealthvar = "net_wealth",
#         filters = filter_three,
#         cumulative = F, # average per percentile
#         probs = c(0,0.25,0.5,0.75,1),
#         descending = F # poorest to richest
#       )
#     })
#   })
# names(WtoI_netwealth) <- allCountries
# 
# WtoI_liquidassets <- allCountries %>%
#   lapply(function(cnt) {
#     mi_point(Wealthfiles, FUN = function(dset) {
#       calc_WtoI(
#         dset,
#         cntr=cnt,
#         wealthvar = "liquid_assets",
#         filters = filter_three,
#         cumulative = F, # average per percentile
#         probs = c(0,0.25,0.5,0.75,1),
#         descending = F # poorest to richest
#       )
#     })
#   })
# names(WtoI_liquidassets) <- allCountries
```

## Gini

### Net Wealth vs Liquid Assets
```{r echo=FALSE, fig.width=11}
tibble(
  net_wealth = Gini_netwealth,
  liquid_assets = Gini_liquidassets
) %>%
  bar_plotter(allCountries)
```

### Net Wealth vs Net Wealth + Offshore
```{r echo=FALSE, fig.width=11}
tibble(
  net_wealth = Gini_netwealth,
  offshore_adjusted = Gini_offshore
) %>%
  bar_plotter(allCountries)
```

### Liquid Assets vs Liquid Assets + Offshore
```{r echo=FALSE, fig.width=11}
tibble(
  liquid_assets = Gini_liquidassets,
  offshore_adjusted = Gini_offshore_liquid
) %>%
  bar_plotter(allCountries)
```

## Distribution Statistics

### Net Wealth
```{r echo=FALSE, fig.height=7, fig.width=7}
Prop_netwealth_asc %>% as_tibble %>% lorenz_plotter
```


```{r echo=FALSE}
Prop_netwealth %>% 
  lapply(formPerc) %>%
  as.data.frame %>%
  kable(format = "html") %>%#booktabs = T format = "latex"
  kable_styling(c("hover", "condensed", "responsive")) %>%
  row_spec(0, hline_after = T) %>%
  column_spec(1, bold = T, border_right = T) %>%
  add_header_above(c("Top % Wealth", "Country" = length(allCountries)))
```

### Liquid Assets
```{r echo=FALSE, fig.height=7, fig.width=7}
Prop_liquidassets_asc %>% as_tibble %>% lorenz_plotter
```


Ordered from richest to poorest percentiles.

```{r echo=FALSE}
Prop_liquidassets %>% 
  lapply(formPerc) %>%
  as.data.frame %>%
  kable(format = "html") %>%#booktabs = T format = "latex"
  kable_styling(c("hover", "condensed", "responsive")) %>%
  row_spec(0, hline_after = T) %>%
  column_spec(1, bold = T, border_right = T) %>%
  add_header_above(c("Top % Wealth", "Country" = length(allCountries)))
```


### Net Wealth Offshore-Adjusted
```{r echo=FALSE, fig.height=7, fig.width=7}
Prop_offshorewealth_asc %>% as_tibble %>% lorenz_plotter
```

Ordered from richest to poorest percentiles.

```{r echo=FALSE}
Prop_offshoreweath %>% 
  lapply(formPerc) %>%
  as.data.frame %>%
  kable(format = "html") %>%#booktabs = T format = "latex"
  kable_styling(c("hover", "condensed", "responsive")) %>%
  row_spec(0, hline_after = T) %>%
  column_spec(1, bold = T, border_right = T) %>%
  add_header_above(c("Top % Wealth", "Country" = length(allCountries)))
```


### Liquid Assets Offshore-Adjusted
```{r echo=FALSE, fig.height=7, fig.width=7}
Prop_liquidoffshorewealth_asc %>% as_tibble %>% lorenz_plotter
```

Ordered from richest to poorest percentiles.

```{r echo=FALSE}
Prop_offshoreweath_liquid %>% 
  lapply(formPerc) %>%
  as.data.frame %>%
  kable(format = "html") %>%#booktabs = T format = "latex"
  kable_styling(c("hover", "condensed", "responsive")) %>%
  row_spec(0, hline_after = T) %>%
  column_spec(1, bold = T, border_right = T) %>%
  add_header_above(c("Top % Wealth", "Country" = length(allCountries)))
```

## Wealth-to-Income

### Wealth to Income Graph - Net Wealth
```{r echo = FALSE}
# WtoI_netwealth %>% 
#   box_plotter
```

### Wealth to Income Table
```{r echo = FALSE}
# WtoI_netwealth %>%
#   as.data.frame %>%
#   kable(format = "html") %>%#booktabs = T format = "latex"
#   kable_styling(c("hover", "condensed", "responsive")) %>%
#   row_spec(0, hline_after = T) %>%
#   column_spec(1, bold = T, border_right = T) %>%
#   add_header_above(c("Top % Wealth", "Country" = length(allCountries)))
```

### Wealth to Income Graph - Net Wealth
```{r echo = FALSE}
# WtoI_liquidassets %>% 
#   box_plotter
```

### Wealth to Income Table
```{r echo = FALSE}
# WtoI_liquidassets %>%
#   as.data.frame %>%
#   kable(format = "html") %>%#booktabs = T format = "latex"
#   kable_styling(c("hover", "condensed", "responsive")) %>%
#   row_spec(0, hline_after = T) %>%
#   column_spec(1, bold = T, border_right = T) %>%
#   add_header_above(c("Top % Wealth", "Country" = length(allCountries)))
```

